%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cies Resume/CV
% LaTeX Template
% Version 1.1 (20/7/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------


\documentclass[10pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)

\include{structure} % Include structure.tex which contains packages and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\maintitle{Mohammad Merajul Islam Molla}{}  % Your name and date of birth or subtitle

\noindent Email: \href{mailto:meraj.enigma@gmail.com}{meraj.enigma@gmail.com}\bull % Your email address
\textsmaller Mobile: {+} (880) 177-682402\bull Skype: mmm2177 \\ % Your phone number(s) and Skype username
LinkedIn: \href{https://www.linkedin.com/in/merajenigma}{https://www.linkedin.com/in/merajenigma} \bull  Github:// \href{https://github.com/imeraj}{\bf imeraj} \\% Your URL
Banani, Dhaka, 1213, Bangladesh % Your address

\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\roottitle{Summary} % Root section title

\vspace{-1.3em} % Reduce whitespace after the Summary heading and the two-column content

\begin{multicols}{2}  % Start a two-column layout
\noindent \textit{About 10 years of industry and academic experience working with diverse technologies ranging from low-level system software to mobile/web applications, project management, company strategy \& policy making, along with new business development and introducing new technologies to meet dynamic nature of tech industry.\\
Have experience working in multiple countries - USA, Japan, India, South Korea and with clients from different countries - USA, South Korea, Japan, and Australia. Good verbal and written communication skills and comfortable working with colleagues and clients from diverse culture.}
\end{multicols}

\noindent{\bf INTERESTS:} New Technology R\&D, Software Architecture, Project Management, Mobile Application Development, Server-side Programming, Software Quality Assurance, Embedded Systems, Recruitment \& Team Building\\

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Experience} % Top level section

%------------------------------------------------
\headedsubsection % Job title entry for the current employer
{\acr{CTO} (Mobile Technology), Monstar Lab Bangladesh, Dhaka, BD}
{Jan 2017 - Oct 2017}
{\bodytext{
\begin{itemize}
\item Supervised Mobile (iOS, Android), Infrastructure, and QA Teams.
\item Supervised projects: Earthcar (\href{http://www.earthcar.co.jp}{http://www.earthcar.co.jp}) Taxi app (Android) - Uber like taxi booking app. Conducted R\&D for iOS app.
\item Conducted regular trainings, tech talks, and internal tech sessions for high performance team building.
\item Was highly involved in recruitment, project estimation, employee evaluation, and company strategy determination.
\end{itemize}
}}

\headedsubsection % Job title entry for the current employer
{Senior Architect (Mobile Technology), Monstar Lab Bangladesh, Dhaka, BD}
{May 2016 - Dec 2016}
{\bodytext{
\begin{itemize}
\item Built and supervised Mobile (iOS, Android) teams from scratch.
\item Worked as Tech Lead and Project Manager for mobile projects (iOS, Android).
\item Supervised projects: A2MILKBAR \- departmental store management app (iOS, Android, PHP/Node.js), Askul (\href{http://www.askul.co.jp}{http://www.askul.co.jp}) - E-commerce App (iOS, Android).
\end{itemize}
}}

\headedsubsection % Job title entry for the current employer
{Chief Engineer (Mobile SW), Samsung R\&D Institute Bangladesh, Dhaka, BD}
{Mar 2014 - May 2016}
{\bodytext{
\begin{itemize}
\item Worked as Tech Lead of Samsung Gear S and Gear Fit Manager applications and managed 20+ team members.
\item Supervised multiple internal projects for iOS, Android and Tizen platforms - Log Analyzer, Emergency Service, TizenFlip, Samsung Guardian App, etc.
\item Managed small team of 3 members to contribution to open source project Linaro.
\end{itemize}
}}

\headedsubsection % Job title entry for the current employer
{Lead Engineer (Mobile SW), Samsung R\&D Institute Bangladesh, Dhaka, BD}
{May 2012 - Mar 2014}
{\bodytext{
\begin{itemize}
\item Worked as Team Lead of Call and Driver Teams of Feature Phone Mobile Commercilisation division and managed around 10+ team members.
\item Worked as Tech Lead of Qshare (Quick Share) project on Android platform.
\end{itemize}
}}

\headedsubsection % Job title entry for the current employer
{System SW Engineer (MAC OS Graphics Driver Team, NVIDIA, CA, USA}
{Jan 2008 - Aug 2011}
{\bodytext{
\begin{itemize}
\item Worked on various components of Display Drivers and core RM Software (Hotplug Architecture, Display Port, Mobile PCI Express Module (MXM), Interrupt Handling, DVI Port, HDCP Protocol, VBIOS, etc).
\item Implemented in C and x86 assembly. 
\end{itemize}
}}

\headedsubsection % Job title entry for the current employer
{MTS Intern (CPD, VMware ESX Server Team), VMware, CA, USA}
{May 2007 - Aug 2007}
{\bodytext{
\begin{itemize}
\item Developed Kernel Crash Dump tool for VMware ESX Server. 
\item Implemented in C and bash script.
\end{itemize}
}}

\headedsubsection % Job title entry for the current employer
{MTS Intern (CPD, VMware ESX Server Team), VMware Inc, CA, USA}
{May 2006 - Aug 2006}
{\bodytext{
\begin{itemize}
\item Developed Filesystem Debugger for VMware ESX Server. 
\item Implemented in C and bash script
\end{itemize}
}}

\spacedhrule{1.8em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\roottitle{Education} % Top level section

\headedsubsection % Job title entry for the current employer
{Marquette University, MS in Computing}
{Dec 2007}
{\bodytext{
\begin{itemize}
\item CGPA: 4.00/4.00
\item Final Project: Implementation of device driver for Broadcom?s BCM4713 Ethernet card on Linksys
WRT54GL router and integrating it with Xinu Kernel.
\end{itemize}
}}

\headedsubsection % Job title entry for the current employer
{BUET, BS in CSE}
{Nov 2004}
{\bodytext{
\begin{itemize}
\item CGPA: 3.92/4.00
\item Thesis: Study of Various Popular Network Simulators and Case Studies using NS-2, Commonly Used Open Source Network Research Simulator, to Simulate Wired and Wireless Networks.
\end{itemize}
}}

\spacedhrule{1.8em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Technical Skills} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Programming Languages:}
{Swift\bull Java\bull Kotlin\bull Ruby\bull Elixir\bull Objective-C\bull C\bull C++\\ Assembly(x86, MIPS)}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Mobile Platforms:}
{iOS\bull Android}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Mobile Architecture Patterns:}
{MVC\bull MVP\bull VIP\bull RxVIP}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Mobile Frameworks/Tools:}
{RxSwift\bull ReSwift\bull RxJava\bull Reductor\bull Alamofire\bull Retrofit 2\bull Gilde\bull Picasso\bull AlamofireImage \bull KingFisher
\bull Firebase\bull Dagger 2\bull ARKit\bull CoreML}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Web Frameworks:}
{Phoenix\bull Ruby on Rails\bull Vapor}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Quality Assurance:}
{Cucumber\bull Calabash\bull XCTest\bull ExUnit\bull MiniTest}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Infrastructure:}
{Docker\bull Nanobox\bull Heroku}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Database:}
{Mysql\bull Sqlite\bull Realm\bull MongoDB\bull Redis}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Project Management:}
{JIRA\bull Redmine\bull Trello}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Version Control:}
{Git\bull Perforce\bull Subversion}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Real-time Services:}
{Pusher\bull PubNub}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Miscelleneous:}
{GraphQL\bull Protobuf\bull Blockchain}


%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%------------------------------------------------

\roottitle{Professional Projects} % Top level section

\headedsubsection
{Earthcar Taxi App (iOS, Android)}
{2017 (Ongoing)}
{\bodytext{
Uber like Taxi app for Earthcar (\href{http://www.earthcar.co.jp}{http://www.earthcar.co.jp}) Japan. Three different
applications - User App (Android, Smartphone), User App (iOS, Smartphone) and Driver App (Android, Tab) along with backend APIs/services and front-end Admin panel.
\begin{itemize}
\item Worked as Tech Lead and Project Manager for mobile apps.
\item Conducted R\&D, designed app architecture, and guided engineers to implement features.
\item Derived project estimation from client requirements, broke down features into sprints, worked with QA Engineers to define test specifications.
\item Conducted code review and managed branch/release policies.
\item Collaborated with backend engineers for smooth integration of APIs/services with mobile apps.
\end{itemize}
}}

\headedsubsection
{Askul E-commerce App (iOS, Android)}
{2017}
{\bodytext{
E-commerce applications developed for Askul (\href{http://www.askul.co.jp}{http://www.askul.co.jp}) Japan. Two different applications - one for iOS and another for Android 
\begin{itemize}
\item Worked as Tech Lead and Project Manager for the project.
\item Conducted R\&D, designed app architecture, and guided developers to implement features.
\item Conducted code review and managed branch/release policies.
\item Backend APIs/services developed using Java (Spring Boot) by 3rd party in Japan.
\item Conducted regular meeting and status reporting with Japan side project stakeholders. 
\end{itemize}
}}


\headedsubsection
{A2MILKBAR App (iOS, Android)}
{2016}
{\bodytext{
Departmental store management app developed for Australian client. Two different applications - one for iOS and another for Android platform along with backend APIs/services and front-end Admin panel.
\begin{itemize}
\item Worked as Tech Lead and Project Manager for the project.
\item Conducted R\&D, designed app architecture, and guided developers to implement features.
\item Conducted code review and managed branch/release policies.
\item Supervised backend APIs/services development using PHP and Node.js.
\end{itemize}
}}

\headedsubsection
{Samsung Gear S and Samsung Gear Fit Apps (iOS)}
{2015-2016}
{\bodytext{
Developed commercial versions of Samsung Gear S and Gear Fit Apps to work with Tizen powered Gear S2 and Gear Fit 2.
\begin{itemize}
\item Developed in collaboration with Samsung HQ (South Korea).
\item Conducted R\&D, designed and developed Basic Accessory Protocol (BAP) on top of Bluetooth Low Energy (BLE).
         The protocol supports - file transfer with pause/resume/cancel, CRC and retransmission, QoS
\item Designed and developed Webproxy module to support multiple Gear apps, such as - Weather, S-Voice, Voice Memo, etc.
\item Notifications using Apple Notification Center Service, along with notification settings, block notifications.
\item Samsung Gear S - \href{https://itunes.apple.com/us/app/samsung-gear-s/id1117310635?mt=8}{https://itunes.apple.com/us/app/samsung-gear-s/id1117310635?mt=8}
\item Samsung Gear Fit - \href{https://itunes.apple.com/us/app/samsung-gear-fit/id1117312500?mt=8}{https://itunes.apple.com/us/app/samsung-gear-fit/id1117312500?mt=8}
\end{itemize}
}}

%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%------------------------------------------------

\roottitle{Academic Projects} % Top level section

\headedsubsection
{Porting (\href{https://github.com/xinu-os/xinu}{Xinu}) Operating System on Linksys WRT54GL Router}
{2006-2007}
{\bodytext{
The purpose of the project is to port Xinu OS, developed at Purdue University, on a modified version of Linksys WRT54GL router. Linksys WRT54GL has BCM947XX chipset with MIPS processor (Broadcom's BCM3302) and comes with OpenWrt Linux distribution.
\begin{itemize}
\item Cisco \& Intel Funded.
\item Implemented exception and interrupt handler for the chipset and integrated it with Xinu.
\item Programmed timer interrupt and integrated it with Xinu's context switch code to enable kernel pre-emption and support process scheduling.
\item Implemented lower-half of interrupt driven asynchronous serial driver (UART 16550) for the router platform.
\item Implemented Ethernet device driver for Broadcom's BCM4713 card on this platform.
\item Implemented in C and MIPS assembly programming languages.
\item Github link - \href{https://github.com/xinu-os/xinu}{https://github.com/xinu-os/xinu}
\end{itemize}
}}

\headedsubsection
{Integrating Speex Codec in Columbia InterNet Extensible Multimedia Architecture (CINEMA)}
{2005}
{\bodytext{
CINEMA is a set of SIP-based Internet Multimedia Servers for creating an Enterprise Telephony and Multimedia system. CINEMA consists of sipd (SIP redirect, proxy, and registrar server), sipconf (SIP Audio Conference Server), sipum (SIP/RTSP unified messaging system), sip323 (SIP-H.323 signaling gateway), rtspd (RTSP streaming media server).
\begin{itemize}
\item Integrated open source speex codec in sipconf conferencing server of CINEMA.
\item Supported two modes of speex codec - narrow-band (8KHz sampling rate) and wide-band (16KHz sampling rate).
\item Fixed several bugs in existing conference server to make the codec work properly within CINEMA architecture.
\item Tested integration of speex codec using Linphone.
\item Implemented in C++ programming language.
\end{itemize}
}}

%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%------------------------------------------------

\roottitle{Open Source Contribution} % Top level section

\headedsubsection
{Linaro Project - \href{http://www.linaro.org}{http://www.linaro.org}}
{2015}
{\bodytext{
Led team of 3 engineers for making contribution to Open Source project (\href{http://www.linaro.org}{Linaro}) - open source software for
ARM SoCs and made decent contribution to their power management tools - powertop, powerdebug, idlestat, and pm-qa.
}}

%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
\roottitle{Achievement/Awards} % Top level section
\begin{longtable}{rl}
2017	   &    Ranked 2nd in Monstar Lab ISUCON Tech Olympics (Web App Performance Tuning contest) \\
2017   &     Promoted as CTO of Mobile Technology Division \\
2015	   &    Won Employee of the Year Award (SRBD)\\
2015	   &    Won Iconic Team award for iOS Gear Manager Team for 2H of Y2015 (SRBD)\\
2014   &    Nominated as Employee of the Year (SRBD)\\
2014	   &    Iconic Team award for Android Development Team for 2H of Y2014 (SRBD)\\
2013   &    Achived Double promotion (promoted from Lead Engineer to Chief Engineer, SRBD) \\
2006-2007 &    Won Graduate Assistantship (Marquette University)\\
1999-2003 &    Won Dean's List Award (BUET)\\
1999-2003 &    Won University Merit Scholarship (BUET)\\
1996-2003 &    Won Board Merit Scholarship (Bangladesh Government)
\end{longtable}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Hobbies} 
{Reading novels, music, movies, travelling}

\end{document}